---
title: "RepData_PeerAssessment1"
author: "Somfay István"
date: "2015. július 19."
output: html_document
---


## Loading and preprocessing the data

Loading and processing data...
```{r loaddata, cache=TRUE}
fileurl <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
temp <- tempfile()
download.file(fileurl,temp, mode="wb")
data <- read.csv(unz(temp, "activity.csv"), header=TRUE, sep=",", na.strings="NA")
unlink(temp)
```
## What is mean total number of steps taken per day?
```{r aggregating}
library(dplyr)
library(ggplot2)
sums <- data %>% group_by(date) %>% summarize(steps = sum(steps, na.rm=TRUE))
mean <- mean(sums$steps)
median <- median(sums$steps)
hist <- ggplot(sums, aes(steps))
hist + geom_histogram(binwidth=(range(sums$steps)[2]/7)) + geom_vline(xintercept=mean, colour="red") + geom_vline(xintercept=median, colour="blue")
```

The total number of steps are aggregated by days. The histogram shows the total number of steps taken each day. The red line shows the mean (`r mean`) and the blue line shows the median (`r median`) of the total number of steps taken per day.

## What is the average daily activity pattern?
```{r average}
minutes <- data %>% group_by(interval) %>% summarize (steps = mean(steps, na.rm=TRUE))
plot(minutes$interval, minutes$steps, type="l", xlab="interval", ylab="average steps")
max <- filter(minutes, steps == max(minutes$steps))[1,1]
```
On average across all the days in the dataset, the `r max` 5-minute interval contains the maximum number of steps.

## Imputing missing values
```{r missing}
nalines <- sum(is.na(data$steps))

```
The total number of missing values are `r nalines`
## Are there differences in activity patterns between weekdays and weekends?